### 2017-02-23 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1650 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

for(D in knitr::opts_current$get()$fig.subcap) {
  hist(runif(100))
}

>>>>

for(D in knitr::opts_current$get()$fig.subcap) {
  hist(runif(100))
}
```

Here is a table

```{r theTable}

mytable = as.data.frame(matrix(runif(6),,3))
names(mytable) = month.name[1:ncol(mytable)]

tableFun = function(...) {
  if(mdToTex) {
    Hmisc::latex(...)
  } else {
    Hmisc::html(...)
  }
}
tableFun(mytable, digits=3, file='',
  caption = 'the table', caption.loc='bottom',
  label = 'tbl:theTable'
    )
